\documentclass[12pt, letter, hidelinks]{article}

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage[none]{hyphenat}  % Disable hyphenation

\pagestyle{empty}
\setlist{nosep}

%==================== CUSTOM ENVIRONMENTS ====================%
\newenvironment{personalInfo}[4]{
  {\bf \LARGE{#1}} \hfill {#2} \\
  {#3} \hfill {#4}
}

\newenvironment{sectionHeader}[1]{
  \vspace{0.1em}  
  {\bf \MakeUppercase{#1}} \vspace{0.25em} \hrule
}

\newenvironment{rSection}[4] {
  \vspace{0.5em}
  {\bf #1} \hfill {\bf #2} \\
  {#3} \hfill {\it #4}
}

%==================== DOCUMENT BEGINS ====================%
\begin{document}

%------------------------ HEADER ------------------------%
\begin{personalInfo}
  {Hishmat Salehi}{\href{mailto:hishmat.salehi2015@gmail.com}{hishmat.salehi2015@gmail.com}}
  {\href{https://github.com/hish-math}{github.com/hish-math}}   {\href{https://www.linkedin.com/in/hishmat-salehi/}{linkedin.com/in/hishmat-salehi/}}\\

\end{personalInfo}

%------------------------ SUMMARY ------------------------%
\begin{sectionHeader}{Professional Summary}\end{sectionHeader}
Technically skilled and curious problem-solver with a strong computer science background.  Passionate about using data and technology to create smart solutions, especially in areas like AI, Business Intelligence, and web development.  Eager to contribute and collaborate on impactful projects.

%------------------------ SKILLS ------------------------%
\begin{sectionHeader}{Skills}\end{sectionHeader}
\begin{tabular}{@{} >{\bfseries}l @{\hspace{1em}} l}
\textbf{Data Analysis \& Visualization} & Power BI, Python, SQL, Streamlit \\
\textbf{Programming Languages}         & Python, Java, JavaScript, Haskell \\
\textbf{Data Science \& Modeling}       & Agent-based Modeling (MESA), Statistical Analysis \\
\textbf{Tools \& Technologies}         & Git, Linux \\
\end{tabular}

%------------------------ EXPERIENCE ------------------------%
\begin{sectionHeader}{Experience}\end{sectionHeader}

\begin{rSection}
{Data Science Student}{}
{PCL Construction}{Jan 2024 - Aug 2024}
\end{rSection}
\begin{itemize}
  \item Designed and developed a \textbf{Python} (Streamlit) web application ("QC Dispatch") to visualize agent-based simulation outcomes, enhancing resource allocation strategies for Quality Control.
  \item Implemented agent-based models utilizing \textbf{Python} (MESA) to simulate project workflows and predict project completion timelines, with simulations projecting up to a 15\% potential increase in operational efficiency. 
\end{itemize}

\begin{rSection}
{Business Systems Analyst II}{}
{McMaster University}{Mar 2022 - Apr 2023}
\end{rSection}
\begin{itemize}
  \item Created and maintained interactive \textbf{Power BI} dashboards delivering critical insights into student recruitment pipelines, including application volume, offer conversion rates, and enrollment forecasts, enabling data-informed strategic planning for university administration.
  \item Managed cloud-based CRM system (Slate) to streamline lead management processes, enhance communication strategies, and generate performance reports.
\end{itemize}

\begin{rSection}
{Teaching Assistant}{}
{McMaster University}{Sep 2021 - Apr 2022 (2 terms)}
\end{rSection}
\begin{itemize}
  \item Taught computer science foundational concepts including: 
	\begin{itemize}
	\item Automata and Computability Theory (Finite State Machines, Regular Expressions)
	\item Introductory Computational Thinking (\textbf{Haskell}, Functional Programming, Recursion).
	\end{itemize}
  \item Facilitated learning for classes of 50+ students, promoting problem-solving skills and analytical thinking.
\end{itemize}

%------------------------ EDUCATION ------------------------%
\begin{sectionHeader}{Education}\end{sectionHeader}

\begin{rSection}
{M.Sc. in Modeling, Data \& Prediction (MDP)}
{Sep 2023 - Apr 2025}
{University of Alberta}
{Edmonton, AB}
\end{rSection}

\begin{rSection}
{B.Sc. in Computer Science (w/ Math minor), cGPA: 3.6/4}
{Sep 2018 - Apr 2022}
{McMaster University}
{Hamilton, ON}
\end{rSection}

\end{document}